### 2021-12-11 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@a34a2edbabf979682451f47ae08b31595d274fc2 🚀
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@f7197e7d0c68bba2b94787cc9bbb29e02090910c 🚀

\begin{figure}
\hypertarget{fig:optimbias}{%
\centering
\includegraphics{figures/optim_mcc_inf.png}
\caption{TODO}\label{fig:optimbias}
}
\end{figure}

Interestingly, as long as the connectance of the network was above
\(\approx 0.1\), the optimal prevalence in the training set is 0.5,
\emph{i.e.} as many positives as negatives. Low connectance is usually
achieved for very large networks, due to the scaling relationship
between richness and links (MacDonald et al., 2020). Therefore, larger
networks may require \emph{more} biasing of the training set in order to
be optimally predicted, whereas smaller, more connected networks may
not. It is worth noting that the optimal bias for the training set
stabilizes at 0.5 regardless of connectance \emph{and} model \emph{and}
measure of model evaluation. \# Guidelines for prediction

INF because we trust positives more than negative, but check with MCC

PR-AUC

usually default to training set bias of 0.5

@@

>>>>

\begin{figure}
\hypertarget{fig:optimbias}{%
\centering
\includegraphics{figures/optim_bias.png}
\caption{TODO}\label{fig:optimbias}
}
\end{figure}

Interestingly, as long as the connectance of the network was above
\(\approx 0.1\), the optimal prevalence in the training set is 0.5,
\emph{i.e.} as many positives as negatives. Low connectance is usually
achieved for very large networks, due to the scaling relationship
between richness and links (MacDonald et al., 2020). Therefore, larger
networks may require \emph{more} biasing of the training set in order to
be optimally predicted, whereas smaller, more connected networks may
not. It is worth noting that the optimal bias for the training set
stabilizes at 0.5 regardless of connectance \emph{and} model \emph{and}
measure of model evaluation.

\begin{figure}
\hypertarget{fig:optimperf}{%
\centering
\includegraphics{figures/optim_perf.png}
\caption{TODO}\label{fig:optimperf}
}
\end{figure}

\hypertarget{guidelines-for-the-assesment-of-network-predictive-models}{%
\section{Guidelines for the assesment of network predictive
models}\label{guidelines-for-the-assesment-of-network-predictive-models}}

The results presented here highlight an interesting paradox: larger
networks (with lower connectance) require more training set bias in
order to maximize model performance fig.~\ref{fig:optimbias}, but are
also more difficult to predict according to MCC and PR-AUC
fig.~\ref{fig:optimperf}. This suggests that the task of network
prediction will be difficult regardless of network size: by being
limited by the \emph{frequency} of interactions when the network is
large, and by being limited by the \emph{number} of interactions when
the network is small. Nevertheless, based on the simulations and
numerical experiments, it is possible to formulate a series of
recommendations for the evaluation of network prediction models.

First, because we should have more trust in reported interactions than
in reported absences of interactions, we can draw on previous literature
to recommend informedness as a measure to decide on a threshold (Chicco
et al., 2021); this being said, because informedness is insensitive to
bias, the model performance is better evaluated through the use of MCC
fig.~\ref{fig:biasmccinf}. Because \(F_1\) is monotonously sensitive to
classifier bias fig.~\ref{fig:bias} and network connectance
fig.~\ref{fig:connectance}, MCC should be prefered as a measure of model
evaluation.

Second, because the PR-AUC responds more to network connectance
fig.~\ref{fig:optimperf} and training set imbalance
fig.~\ref{fig:biasrocpr}, it should be used as a measure of model
performance over the ROC-AUC. This is not to say that ROC-AUC should be
discarded (in fact, a low ROC-AUC is a sign of an issue with the model),
but that its interpretation should be guided by the PR-AUC value. This
again echoes recommendations from other fields (Saito \& Rehmsmeier,
2015).

Thirdly, regardless of network connectance \emph{or} measure to evaluate
the model performance, as long as the network connectance is larger than
\(\approx 0.1\), artificially balancing the training set to have
equiprevalence will give the best possible results. This was true for
all models.

Finally, it is noteworthy that the ensemble model was systematically
better than the component models; even when poor models were included
(Random Forest and Decision Tree), the ensemble was able to leverage the
different biases expressed by the models to make an overall more
accurate prediction. We do not expect that ensembles will \emph{always}
be better than single models. In a recent multi-model comparison, Becker
et al. (2021) found that the ensemble was \emph{not} the best model.
There is no general conclusion to draw from this besides reinforcing the
need to be pragmatic about which models should be included in the
ensemble, or whether to use an ensemble at all. In a sense, the
surprising peformance of the ensemble model should form the basis of the
last recommendation: optimal training set bias and its interaction with
connectance and binary classifier is, in a sense, an hyperparameter that
should be assessed. The distribution of results in
fig.~\ref{fig:optimbias} and fig.~\ref{fig:optimperf} show that there
are variations around the trend; furthermore, networks with different
structures than the one we simulated here may respond in different ways.

@@

\leavevmode\hypertarget{ref-Becker2021OptPre}{}%
Becker, D., Albery, G. F., Sjodin, A. R., Poisot, T., Bergner, L.,
Dallas, T., Eskew, E. A., Farrell, M. J., Guth, S., Han, B. A., Simmons,
N. B., Stock, M., Teeling, E. C., \& Carlson, C. J. (2021). Optimizing
predictive models to prioritize viral discovery in zoonotic reservoirs.
\emph{bioRxiv}, 2020.05.22.111344.
\url{https://doi.org/10.1101/2020.05.22.111344}
